%-------------------------
% Resume in Latex
% Author : Jorge Garcia
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}



%------------------------------------------
%custom underlilne package
\usepackage[normalem]{ulem}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Jorge Garcia} \\ \vspace{1pt}
    \small \href{mailto:jorge.gar@me.com}{\uline{jorge.gar@me.com}} $|$ 
    \small \href{mailto:jorge.gar@me.com}{\uline{NY based}} $|$ 
    \href{https://cyberdevpro.com}{\uline{cyberdevpro.com}} $|$
    \href{https://github.com/kawa5604/}{\uline{github.com/kawa5604}} $|$
\end{center}



%-----------EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart


      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Cybersecurity Analyst \& Penetration Tester}{2021 -- Current}
      {Dox Electronics}{NY}
      \resumeItemListStart
        \resumeItem{Perform audits for Defense Industrial Base (DIB) companies seeking \emph{CMMC, NIST 800-171, NIST SP 800-53, and NY SHIELD} compliance.}
        \resumeItem{Perform all phases of \emph{internal and external penetration testing.}}
        \resumeItem{Successfully completed \emph{Red Team engagements} including physical security control testing.}
        \resumeItem{Designed, developed, and maintained internal SOP web application to \emph{optimize the customer auditing process.}}
        \resumeItem{Perform \emph{web application testing} based on OWASP TOP 10 framework.}
        \resumeItem{Designed and implemented a \emph{new product} for customers seeking phishing testing and training.}
        \resumeItem{Designed, developed, and implemented a new recurring revenue product to perform routine vulnerability assessments on customer internal networks.}
        \resumeItem{Perform \emph{Email Data Leak} audits on multiple cloud platforms and vendors.}
        \resumeItem{Perform \emph{Cloud audits} on AWS and Azure, both hybrid and pure-cloud environments.}
        \resumeItem{Delivered  \emph{custom written reports and presentations} to customers and stakeholders with findings.}
        \resumeItem{Perform \emph{Man-in-the-Middle} attacks and \emph{wireshark} packet analysis to recover SMB objects, VoIP phone calls, print jobs, etc.}
        \resumeItem{Perform \emph{OSINT} reconnaisance for a more comprehensive \emph{external threat footprint} overview for customers and C-level executives.}
        \resumeItem{Write reports with \emph{actionable intelligence} and \emph{action items} that translated to more secure client organizations.}
        \resumeItem{Develop automation tools to perform email spoofing and relaying attacks for phishing campaigns.}
        \resumeItem{Help customers with Incident Response by request.}
    \resumeItemListEnd

    \resumeSubheading
      {Jr Dev-Ops Engineer}{2019 -- 2021}
      {University of Nevada Las Vegas}{Las Vegas, NV}
      \resumeItemListStart
        \resumeItem{Maintain and monitor workstations, labs, student-facing servers, faculty-facing servers, and networks for the Dept. of Computer Science.}
        \resumeItem{Assess and troubleshoot computer problems brought by students, faculty and staff.}
        \resumeItem{Develop new web-apps for monitoring and logging and automate processes and procedures.}
        \resumeItem{Monitor internal subnet for intrusions and develop documentation and procedures for incident response.}
        \resumeItem{Implemented an internal inventory system web application - \emph{python, flask, PSQL}}
    \resumeItemListEnd

    \resumeSubheading
      {Intern}{2021-- 2021}
      {Maryland Innovation and Security Institute}{Remote}
      \resumeItemListStart
        \resumeItem{Intern for the \emph{Cyber Education Diversity Cybership}}
        \resumeItem{Build skills in network and log analysis at a Security Operations Center \emph{SOC}}
        \resumeItem{Complete the Cybersecurity Maturity Model Certification \emph{CMMC}}
      \resumeItemListEnd
      
      \resumeSubheading
      {Undergraduate Research Assistant}{2020 -- 2021}
      {University of Nevada Las Vegas}{Las Vegas, NV}
      \resumeItemListStart
        \resumeItem{Researched Optical Character Recognition and developed a plugin to read, parse, and analyze data on a web application.}
        \resumeItem{Developed a social distancing detector using Deep Learning, OpenCV, and YOLOv3. Paper published by UNLV.}
        \resumeItem{Developed a polaroid filter extraction application using Conditional Adversarial Networks and OpenCV paper published by ITNG.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Officer}{2019 -- 2021}
      {Layer Zero Cybersecurity Club}{Las Vegas, NV}
      \resumeItemListStart
        \resumeItem{Hosted an instance of OWASP's Security Shepherd web-app to develop cybersecurity skills.}
        \resumeItem{Manage and post on the club's website and blog.}
        \resumeItem{Publish write-ups to CTF exercises.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Volunteer}{2021 - 2021}
      {Cimarron Memorial High School}{Las Vegas, NV}
      \resumeItemListStart
        \resumeItem{Mentor High School students from their cybersecurity club.}
        \resumeItem{Teach basics and introductory cybersecurity terminology and concepts.}
      \resumeItemListEnd

    \resumeSubheading
      {Volunteer}{ 2019 --  2020}
      {OWASP}{Las Vegas, NV}
      \resumeItemListStart
        \resumeItem{Volunteer setting up quarterly meetings and cybersecurity conferences.}
        \resumeItem{Attend cybersecurity conferences to promote OWASP.}
      \resumeItemListEnd
      

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Nevada Las Vegas}{Las Vegas, NV}
      {Bachelor of Science in Computer Science - Cybersecurity Concentration}{May 2021}
    \resumeSubheading
      {La Salle University}{Mexico}
      {Bachelor of Business Administration}{May 2012}
  \resumeSubHeadingListEnd



%-----------PROJECTS-----------
%\section{Projects}
 %   \resumeSubHeadingListStart
  %    \resumeProjectHeading
   %       {\textbf{Flix} $|$ \emph{Swift, UIkit, Cocoapods, web API,}}{June 2020 -- Present}
    %      \resumeItemListStart
    %        \resumeItem{Developing an iOS app to parse an API to list most recent and coming-soon movies.}
    %        \resumeItem{Implemented GitHub OAuth to get data from user’s repositories}
    %        \resumeItem{Visualized GitHub data to show collaboration}
    %        \resumeItem{Used Celery and Redis for asynchronous tasks}
    %      \resumeItemListEnd
     % \resumeProjectHeading
     %     {\textbf{Home-Lab} $|$ \emph{Internal DNS, VPN, DHCP, virtual pfSense routers, puppet CMS, Wireless APs}}{March 2020 -Present}
     %     \resumeItemListStart
     %       \resumeItem{Built my own home-lab and network to practice cybersecurity concepts securely.}
     %       \resumeItem{Set up multiple virtual networks to isolate devices.}
     %       \resumeItem{Manage my local PKI with a root CA to sign on my internal web-apps for testing.}
     %       \resumeItem{Unbound DNS, DHCP, and VPN handled by different vms.}
     %       \resumeItem{Hosting my instance of OWASP Security Shepherd and FacebookCTF.}
     %       \resumeItem{Practice concepts like network analysis with Wireshark, wireless AP wep/wpa attacks, MITM attacks, system hardening}
     %     \resumeItemListEnd
    % \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills and Toolsets}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Swift, Bash, Java, Python, SQL, JavaScript, HTML/CSS} \\
     \textbf{Frameworks}{: SwiftUI, UIKit } \\
     \textbf{Developer Tools}{: Git, Docker, ELK stack, Puppet Technologies, Ovirt Virtualization Manager, Proxmox, Active Directory,  AWS, AZURE, Google Cloud Platform, multiple linux distributions, Wireshark, Nagios Monitoring} \\
     \textbf{Tools}{: Nessus, BurpSuite, ZAP, Ghidra, IDA Pro, Wireshark, Nmap, msf, greenbone}
    }}
 \end{itemize}


%
%-----------CEERTIFICATIONS----------
\section{CERTIFICATIONS \& RELEVANT COURSES  }
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{\href{https://activecountermeasures.com}{\underline{Active Countermeasures}}}{: Threat Hunting} \\
     \textbf{Google - Coursera}{: Technical Fundamentals, Python and OS', Config. Management and the Cloud} \\
     \textbf{\href{https://codepath.org}{\underline{CodePath}}}{: iOS  Development} \\
     \textbf{\href{https://codepath.org}{\underline{CodePath}}}{: Cybersecurity} \\
     \textbf{NASA - Desert Research Institute}{: Cybersecurity Bootcamp} \\
     \textbf{UNLV - Graduate School}{: Digital Forensics} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
